PANCHANGE_analysis

### 2020-09-30 PANCHANGE_analysis.Rmd
violin plots for, phq, gad, ocir

@@

@@

@@

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed",
                            "Ethnicity_collapsed",
                            "time_diff_coping_lockdown_march_23"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker_numeric",
                             "time_diff_coping_lockdown_march_23"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_coping_lockdown_march_23"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

#GAD baseline, not controlling for prior symptoms
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a absolute whole sample}
# Regression coefficients
gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_estimates)
gad_baseline_model0a_estimates

# Regression diagnostic statistics
gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0a_reg_stats)
gad_baseline_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad model0b absolute whole sample}
# Regression coefficients
gad_baseline_model0b_estimates <- model0b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0b_estimates)
gad_baseline_model0b_estimates

# Regression diagnostic statistics
gad_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model0b_reg_stats)
gad_baseline_model0b_reg_stats
```

>>>>

### Violin plots

```{r gad.sum violin plot}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")
) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  coord_flip()
```

```{r gad.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
             ) +
  coord_flip()
```

```{r gad.sum violin plot Disorder_hierarchical}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
             ) +
  coord_flip()
```

@@

### Violin plots

```{r phq.sum violin plot}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")
  ) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  coord_flip()
```

```{r phq.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r phq.sum violin plot Disorder_hierarchical}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```

@@

### Violin plots

```{r ocir.sum violin plot}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")
  ) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  coord_flip()
```

```{r ocir.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r ocir.sum violin plot Disorder_hierarchical}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```

@@

```{r model1a function}
model1a.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("Disorder_hierarchical",
                            "Gender_collapsed",
                            "age_category_collapsed",
                            "Ethnicity_collapsed",
                            "time_diff_sign_up_coping"
                            )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,"model1a_estimates"),
         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"

@@

```{r model1a.explan function}
model1a.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "Disorder_hierarchical",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@

  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
           mutate(
             "Indepent variable" = recode_factor(
               term,
               "(Intercept)" = "Intercept",
               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
               "Disorder_hierarchicalEating disorders" = "Eating disorders",
               "Disorder_hierarchicalOCDs" = "OCDs",
               "Disorder_hierarchicalPTSD" = "PTSD",
               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
               "Gender_collapsedFemale" = "Female",
               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
               "Ethnicity_collapsedAfrican or African British" = "African or African British",
               "Ethnicity_collapsedOther" = "Other ethnicity",
               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
             ),
             "Estimate" = format(
               round(estimate,
                     digits = 2),
               nsmall = 2),
             "95% CI low" = format(
               round(conf.low,
                     digits = 2),
               nsmall = 2),
             "95% CI up" = format(
               round(conf.high,
                     digits = 2),
               nsmall = 2),
             "SE" = format(
               round(std.error,
                     digits = 2),
               nsmall = 2),
             "z score" = format(
               round(statistic,
                     digits = 2),
               nsmall = 2),
             "p value" = case_when(
               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
             )
           ) %>%
           select(
             "Indepent variable",
             "Estimate",
             "95% CI low",
             "95% CI up",
             "SE",
             #    "z score",
             "p value"
           )
  )

@@

```{r model1b.explan function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "time_diff_sign_up_coping"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula

@@
